Reflections from reproductions

### 2024-10-16 pages/reflections.qmd
docs(reflections): add wood 2021

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@anagnostou_facs-charm_2022: Partially met (depending on how strict you are being). The Python version was stated in the paper, and the simpy version was stated in the complementary app repository (although neither were mentioned in the model repository itself).

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

* It can be quite difficult to change parameters that are hard coded into the model. Ideally, all the parameters that a user might want to change should be easily changeable and not hard coded.
* This is a somewhat common issue.
* There is overlap between this and whether the code for scenarios is provided (as typically, the code for scenario is conditionally changing parameter values, although this can be facilitated by not hard coding the parameters, so you call need to change the values from "outside" the model code, rather than making changes to the model functions themselves). Hence, have included as two seperate reflections.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@johnson_cost_2021: Fully met.

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

## Run time and memory usage

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* @huang_optimizing_2019: No changes made.
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
* @johnson_cost_2021: <!--TODO-->

@@

@wood_value_2021: <!--TODO-->

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

@wood_value_2021: <!--TODO-->

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@lim_staff_2020, @anagnostou_facs-charm_2022: Not applicable (no in-text results).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@wood_value_2021: <!--TODO-->

>>>>

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ❌ |

@@

@wood_value_2021: Not met. However, easily resolved based on imports to `.R` script.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | 🟡 |

@@

@anagnostou_facs-charm_2022: Partially met (depending on how strict you are being). The Python version was stated in the paper, and the SimPy version was stated in the complementary app repository (although neither were mentioned in the model repository itself).

@@

@wood_value_2021: Partially met. States version of R but not package. Due to prior issues with backdating R, used latest versions. There were no issues using the latest versions of R and packages, but if there had been, it would be important to know what versions had previously been used and worked.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@wood_value_2021: Fully met. Provided as a single `.R` file which ran the model with a for loop.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@wood_value_2021: Fully met. Changes inputs to run all scenarios from a single `.R` file.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | ✅ |

@@

@wood_value_2021: Fully met. All model parameters for the scenarios/sensitivity analysis could be varied from "outside" the model code itself.

@@

* It can be quite difficult to change parameters that are hard coded into the model. Ideally, all the parameters that a user might want to change should be easily changeable and not hard coded.
* This is a somewhat common issue.
* There is overlap between this and whether the code for scenarios is provided (as typically, the code for scenario is conditionally changing parameter values, although this can be facilitated by not hard coding the parameters, so you call need to change the values from "outside" the model code, rather than making changes to the model functions themselves). Hence, have included as two seperate reflections.
* Important to note that we evaluate this in the context of reproduction - and have not checked for hard-coded parameters outside the specified scenario analyses, but that someone may wish to alter if reusing the model for a different analysis/context/purpose.

## Use relative file paths

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |

@shoaib_simulation_2021: <!--TODO-->

@huang_optimizing_2019: <!--TODO-->

@lim_staff_2020: <!--TODO-->

@kim_modelling_2021: <!--TODO-->

@anagnostou_facs-charm_2022: <!--TODO-->

@wood_value_2021: Fully met. Although I then changed things a bit as reorganised repository and prefer not to work with `setwd()`, these were set up in such a way that it would be really easy to correct file path, just by setting working directory at start of script.

**Reflections:** <!--TODO: Update reflections (when add Shoaib, Huang, Lim, Kim and Wood) and then (since have added Johnson, Hernandez and Wood) -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@@

@wood_value_2021: Fully met.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | ❌ |

@@

@wood_value_2021: Not met. Very few comments, so for the small bit of the code that I did delve into, took a bit of working out what different variables referred to.

@@

## Run time, memory usage and file size

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* @huang_optimizing_2019: No changes made.
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: <!--TODO-->
* @wood_value_2021: No changes made, but unlike other reproduction, didn't try to run at smaller amounts - just set it to run as-is over the weekend.

@@

@@

## Avoid large file sizes if possible

I have not evaluated like as a criteria, as a large file size is not inherently a bad thing, and might be difficult to avoid. However, when files are very large, this can make things trickier, such as with requiring compression and use of GitHub Large File Storage (LFS) for tracking, which has limits on the free tier.

Regarding file sizes in each study:

* @shoaib_simulation_2021: <!--TODO-->
* @huang_optimizing_2019: <!--TODO-->
* @lim_staff_2020: <!--TODO-->
* @kim_modelling_2021: <!--TODO-->
* @anagnostou_facs-charm_2022: <!--TODO-->
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: <!--TODO-->
* @wood_value_2021: Aggregate results files are small (327 kB), but raw results files are very large (2.38 GiB), and even when compressed to `.csv.gz` (128 MiB) require using of GitHub LFS

**Reflections:** <!--TODO: Update reflections (when add Shoaib, Huang, Lim, Kim and Wood) and then (since have added Johnson, Hernandez and Wood) -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | 🟡 |

@@

@wood_value_2021: Partially met. In the paper, they state that it takes less than five minutes for each scenario, but this feels like half the picture, given the total run time was 48 hours.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

@wood_value_2021: Not applicable. As stated in their prior paper, the model is constrained by processing time, not computer memory.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

@wood_value_2021: Not applicable. All provided.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@wood_value_2021: Outputs to `.csv` files.

@@

@wood_value_2021: Fully met. I didn't need to work with the output tables, but from looking at them now, they make sense.

@@

@wood_value_2021: Fully met. Sets seed based on replication number.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@wood_value_2021: Fully met. Figures match article, with one minor exception that I had to add smoothing to the lines on one of the figures.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

@lim_staff_2020, @anagnostou_facs-charm_2022, @wood_value_2021: Not applicable (no in-text results).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | ❌ |

@@

@wood_value_2021: Not met. No instructions, although it was fairly self explanatory (single script `master.R` to run, then processing scripts named after items in article e.g. `fig7.R`).
